\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-18 paper.tex
Added interp citation

Delaunay triangulation \citep{lee1980} (XXXREF what R package are you
using?) is used to connect neighboring centroids. The edges are needed
to preserve neighborhood information when the model is lifted into
\pD{}.

>>>>

Delaunay triangulation \citep[@albrecht2024]{lee1980} is used to connect
neighboring centroids. The edges are needed to preserve neighborhood
information when the model is lifted into \pD{}.
